CASTRO: A New Compressible Astrophysical Solver. IV. Performance Portability and GPUs

### 2019-03-28 gpus/paper.tex
translate slack discussion

>>>>

\section{Runtime Considerations}

Volta can have as many as 160k threads in flight at any one time,
whereas a $32^3$ box of cells is 30k.  This means that we haven't
exposed enough parallelism to keep the device busy.  Generally we
launch each box in a separate stream so it's often OK to do this, but
other times this is a bottleneck, and we need bigger boxes for best
performance.
